SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-16 scipy-1.0/paper.tex
decisive doesn't seem like the right word -> auspicious

Yet, the philosophical motivations behind a fully open toolstack, and
an excited, friendly community with a singular focus, seemed to have
proven decisive in the long run.  It led not only to the library
described in this paper, but also to an entire ecosystem of related
packages \cite{scipy-ecosystem}, and a variety of social activities centered around
them\cite{social-python}. The packages in the SciPy ecosystem 
share high standards of implementation,
documentation, and testing, and a culture eager to learn and adopt
better practices---both for community management and software
development.

>>>>

Yet, the philosophical motivations behind a fully open toolstack, and
an excited, friendly community with a singular focus, seemed to have
proven auspicious in the long run.  It led not only to the library
described in this paper, but also to an entire ecosystem of related
packages \cite{scipy-ecosystem}, and a variety of social activities centered around
them\cite{social-python}. The packages in the SciPy ecosystem 
share high standards of implementation,
documentation, and testing, and a culture eager to learn and adopt
better practices---both for community management and software
development.
